An Open System for\\ Managing Short Programming Exercises

### 2013-08-08 paper/talk.tex
move screenshot
added new screenshot
a few tweaks

\begin{itemize}
  \item Many students struggle in introductory programming courses
  \item Mastery of basic concepts and techniques is essential for success
  \item Short programming exercises:
  \begin{itemize}
    \item Students write or complete a short (5-15 line) program
    \item Interface is typically web-based
    \item Correctness is judged with a series of test cases
    \item Student receives immediate feedback about results of tests
  \end{itemize}
  \item Exercises are useful for:
  \begin{itemize}
    \item Skills development
    \item Self-tests to accompany reading
    \item Extra practice
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
  \item Analogy: learning programming vs.\ learning to play a musical instrument
  \item Larger assignment (like SIGCSE {\em Nifty Assignments}) :: Recital piece
  \item Short exercise :: Playing a scale
\end{itemize}

@@

\begin{itemize}
  \item The impact of a pedagogical technique or curriculum material
        depends on how many students are exposed to it
  \item Systematically eliminating barriers to adoption maximizes impact
  \begin{itemize}
    \item Requiring payment is a barrier to adoption
    \item Restrictive licenses are a barrier to adoption
    \item Control by a central authority is a barrier to adoption
  \end{itemize}
  \item Ideal situation: resources are available to anyone at any time for any purpose
%  \item Case in point...
\end{itemize}

@@

\begin{itemize}
  \item Open source (AGPL v3)
  \item Supports exercises in Java, Python, Ruby, and C/C++
  \item Collects fine-grained edit sequence of each student's work
  \item Repository of freely-redistributable (CC-BY-SA) exercises:
        \url{https://cloudcoder.org/repo}
\end{itemize}

\begin{itemize}
  \item Requires two Linux servers to host (one network-facing)
    \begin{itemize}
    \item Relatively easy to install
    \item Known to support 60+ concurrent users with modest hardware
    \item Load testing experiments successful with 700+ concurrent users
          on moderate server hardware
      \begin{itemize}
      \item Compiling and testing submissions requires significant
            CPU resources, but is easy to scale up by adding more
            build servers
      \end{itemize}
    \item Cost to host per course-semester: perhaps \$1-\$3 per student
          (e.g., using Amazon EC2)
    \end{itemize}
  \item {\bf We can host CloudCoder for your course!}
    \begin{itemize}
    \item We have a grant from Amazon to cover hosting costs for
          a small number of institutions/courses
    \item {\bf Talk to us if you are interested!}
    \end{itemize}
\end{itemize}

@@

>>>>

\begin{itemize}
  \item Many students struggle in introductory programming courses
  \item Mastery of basic concepts and techniques is essential for success
  \item Short programming exercises ({\it {\` a} la} CodingBat):
  \begin{itemize}
    \item Students write or complete a short (5-15 line) program
    \item Interface is typically web-based
    \item Correctness is judged with a series of test cases
    \item Student receives immediate feedback about results of tests
  \end{itemize}
  \item Exercises are useful for:
  \begin{itemize}
    \item Skills development
    \item Self-tests to accompany reading
    \item Extra practice
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
  \item Analogy: learning programming vs.\ learning to play a musical instrument
  \item Larger assignment (like SIGCSE {\em Nifty Assignments}) :: Recital piece
  \item Short exercise :: Playing a scale, an {\' e}tude
\end{itemize}

@@

\begin{itemize}
  \item The impact of a pedagogical technique or curriculum material
        depends on how many students are exposed to it
  \item Systematically eliminating barriers to adoption maximizes impact
  \begin{itemize}
    \item Requiring payment is a barrier to adoption
    \item Restrictive licenses are a barrier to adoption
    \item Control by a central authority is a barrier to adoption
  \end{itemize}
  \item Ideal situation: resources are available to {\bf anyone} at {\bf any time} for {\bf any purpose}
%  \item Case in point...
\end{itemize}

@@

\begin{itemize}
  \item Open source (AGPL v3)
  \item Web-based user interface
    \begin{itemize}
    \item 100\% HTML/CSS/JavaScript, no plugin required
    \end{itemize}
  \item Supports exercises in Java, Python, Ruby, and C/C++
  \item Collects fine-grained edit sequence of each student's work
  \item Repository of freely-redistributable (CC-BY-SA) exercises:
        \url{https://cloudcoder.org/repo}
\end{itemize}

@@

\begin{itemize}
  \item Requires two Linux servers to host (one network-facing)
    \begin{itemize}
    \item Relatively easy to install
    \item Known to work: 60+ concurrent users with modest hardware
    \item Load testing: with 700+ concurrent users
          on moderate server hardware
      \begin{itemize}
      \item Compiling and testing submissions requires significant
            CPU resources, but is easy to scale up by adding more
            build servers
      \end{itemize}
    \item Cost to host per course-semester: perhaps \$1-\$3 per student
          (e.g., using Amazon EC2)
    \end{itemize}
  \item {\bf We can host CloudCoder for your course!}
    \begin{itemize}
    \item We have a grant from Amazon to cover hosting costs for
          a small number of institutions/courses
    \item {\bf Talk to us if you are interested!}
    \end{itemize}
\end{itemize}
